Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-03-05 paper/current/main.tex

%
% SUBSECTION: DISTANCE
%
\subsection{Distance}
%% Distance calculations
We calculate $f_{ij}$, the pairwise number of co-affiliations between organizations, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories. 
For example, $f_{ij} = 10$ indicates that ten authors were co-affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications. 
In contrast to traditional mobility studies, all co-affiliations are symmetric, meaning that $f_{ij} = f_{ji}$.

@@

We model the flux of authors between organizations, $f_{ij}$, using the gravity law. 
the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
Following the gravity law, the expected flux $\widetilde{f_{ij}}$ between two organizations is defined as follows,

\begin{equation}
	\label{eq:gravity_basic}
	\widetilde{f_{ij}} = C*m_{i}m_{j}*f(r_{ij})
\end{equation}

@@

\begin{equation}
	\label{eq:linear_flux_geo}
	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C)  - \alpha \ln(g_{ij})
\end{equation}

\begin{equation}
	\label{eq:linear_flux_emb}
	\ln(\frac{f_{ij}}{m_im_j}) = \ln(C) - \beta d_{ij}
\end{equation}

where $f_{ij}$ is the real flux from dataset. The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.
This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
We follow standard practice and exclude from our analysis zero flows.

>>>>

%
% SUBSECTION: DISTANCE
%
\subsection{Distance}
%% Distance calculations
We calculate $T_{ij}$, the pairwise number of co-affiliations between organizations, calculated as the number of co-occurrences of organizations within author co-affiliation trajectories. 
For example, $T_{ij} = 10$ indicates that ten authors were co-affiliated with both organization $i$ and $j$ between 2008 and 2019, as evidenced from their publications. 
In contrast to traditional mobility studies, all co-affiliations are symmetric, meaning that $T_{ij} = T_{ji}$.

@@

We model the flux of authors between organizations, $T_{ij}$, using the gravity law. 
the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\autocite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
Following the gravity law, the expected flux $\hat{T_{ij}}$ between two organizations is defined as follows,

@@

\begin{equation}
	\label{eq:linear_flux_geo}
	\ln(\frac{T_{ij}}{m_im_j}) = \ln(C)  - \alpha \ln(g_{ij})
\end{equation}

\begin{equation}
	\label{eq:linear_flux_emb}
	\ln(\frac{T_{ij}}{m_im_j}) = \ln(C) - \beta d_{ij}
\end{equation}

where $T_{ij}$ is the real flux from dataset. The gravity law of mobility is known to be sensitive to the case where $T_{ij} = 0$, or zero movement between organizations. 
Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.
This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \autocite{simini2012universal}.
We follow standard practice and exclude from our analysis zero flows.
